---
title: "Brighton Restaurant Awards (BRAVO) 2026 — Interactive Map"
author: "Adam Dennett"
format:
  html:
    output-file: index.html
    page-layout: full
    toc: false
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(leaflet)
library(htmlwidgets)
library(htmltools)
library(jsonlite)

winners <- read_csv("bravo_2026_winners.csv", show_col_types = FALSE)
venues  <- read_csv("bravo_2026_venues.csv",  show_col_types = FALSE) |>
  mutate(lat = as.numeric(lat), lon = as.numeric(lon))

first_nonempty <- function(x) {
  x <- x[!is.na(x) & x != ""]
  if (length(x) == 0) "" else x[[1]]
}

venues_for_map <- winners |>
  filter(!is.na(lat), !is.na(lon)) |>
  group_by(venue_idx) |>
  summarise(
    name        = first(name),
    profile_url = first_nonempty(profile_url),
    venue_url   = first_nonempty(venue_url),
    address     = first_nonempty(address),
    postcode    = first_nonempty(postcode),
    lat         = first(lat),
    lon         = first(lon),
    rankings    = list(tibble(category = category, rank = rank)),
    best_rank   = min(rank),
    n_cats      = n(),
    .groups     = "drop"
  )

# Jitter venues sharing exact lat/lon (~5.5 m circle)
venues_for_map <- venues_for_map |>
  mutate(.coord_key = paste0(round(lat, 5), "_", round(lon, 5))) |>
  group_by(.coord_key) |>
  mutate(
    .n   = n(),
    .ix  = row_number() - 1,
    .ang = ifelse(.n > 1, 2 * pi * .ix / .n, 0),
    .r   = ifelse(.n > 1, 0.00005, 0),
    lat  = lat + .r * cos(.ang),
    lon  = lon + .r * sin(.ang) / cos(lat * pi / 180)
  ) |>
  ungroup() |>
  select(-.coord_key, -.n, -.ix, -.ang, -.r)

categories <- sort(unique(winners$category))

icon_base <- "https://img.restaurantsbrighton.co.uk"
category_icons <- c(
  "Best Brighton Restaurant"   = paste0(icon_base, "/wp-content/uploads/2019/11/best-restaurant.png"),
  "Best Sussex Restaurant"     = paste0(icon_base, "/wp-content/uploads/2016/11/best-restaurant.jpg"),
  "Best Brunch"                = paste0(icon_base, "/wp-content/uploads/2023/03/brunch-1.png"),
  "Plant Champions"            = paste0(icon_base, "/wp-content/uploads/2019/11/plant-champions.png"),
  "Best Cocktails"             = paste0(icon_base, "/wp-content/uploads/2023/03/cocktails.png"),
  "Best Brighton Pub"          = paste0(icon_base, "/wp-content/uploads/2023/03/Best-local-1.png"),
  "Family Friendly"            = paste0(icon_base, "/wp-content/uploads/2023/03/for-the-family-1.png"),
  "Best Team"                  = paste0(icon_base, "/wp-content/uploads/2023/03/best-team-1.png"),
  "Best Sussex Pub"            = paste0(icon_base, "/wp-content/uploads/2019/11/best-pub-grub.png"),
  "Best Cafe"                  = paste0(icon_base, "/wp-content/uploads/2023/03/best-cafe-1.png"),
  "Best Lunch"                 = paste0(icon_base, "/wp-content/uploads/2024/01/lunch-2.png"),
  "Best Sunday Roast"          = paste0(icon_base, "/wp-content/uploads/2023/03/sunday-roast.png"),
  "Best Wine List"             = paste0(icon_base, "/wp-content/uploads/2023/03/wine-list.png"),
  "Best International Cuisine" = paste0(icon_base, "/wp-content/uploads/2023/03/international.png"),
  "Sustainability Champions"   = paste0(icon_base, "/wp-content/uploads/2023/03/sustainable.png"),
  "Best Value"                 = paste0(icon_base, "/wp-content/uploads/2023/03/Eat-well-for-less-1.png"),
  "Best Takeaway"              = paste0(icon_base, "/wp-content/uploads/2024/01/takeaway-2.png"),
  "Sweets and Treats"          = paste0(icon_base, "/wp-content/uploads/2026/03/sweet-treat-1-4.png")
)
```

Voted by 71,285 locals in March 2026. **`r nrow(venues_for_map)`** geocoded venues across **`r length(categories)`** categories.

Use the dropdowns to filter the map by category, rank range, or specific venue. When a category is selected, markers use that category's BRAVO icon on a brand-lime badge; "All categories" falls back to Spectral-coloured circles sized by best rank.

```{r bravo-map}
venue_data <- venues_for_map |>
  rowwise() |>
  mutate(
    cats  = list(rankings$category),
    ranks = list(rankings$rank)
  ) |>
  ungroup() |>
  select(name, address, postcode, lat, lon, profile_url, venue_url,
         best_rank, n_cats, cats, ranks)

data_json  <- toJSON(venue_data, na = "null", auto_unbox = TRUE, dataframe = "rows")
cats_json  <- toJSON(c("All categories", categories), auto_unbox = TRUE)
icons_json <- toJSON(as.list(category_icons), auto_unbox = TRUE)

m <- leaflet(width = "100%", height = 700) |>
  addProviderTiles(providers$CartoDB.Positron) |>
  setView(lng = -0.139, lat = 50.825, zoom = 13)

data_tag <- htmltools::tags$script(
  type = "application/json",
  id   = "bravo-venue-data",
  htmltools::HTML(as.character(data_json))
)

font_tag <- htmltools::tagList(
  htmltools::tags$link(rel = "preconnect", href = "https://fonts.googleapis.com"),
  htmltools::tags$link(rel = "preconnect", href = "https://fonts.gstatic.com", crossorigin = ""),
  htmltools::tags$link(rel = "stylesheet",
    href = "https://fonts.googleapis.com/css2?family=Open+Sans:wght@400;600;700&family=Questrial&display=swap")
)

style_tag <- htmltools::tags$style(htmltools::HTML('
  body, .quarto-container, p { font-family: "Open Sans", "Helvetica Neue", Helvetica, Arial, sans-serif; color: #000; }
  h1, h2, h3, h4, h5, h6, .title { font-family: Questrial, "Helvetica Neue", Helvetica, Arial, sans-serif; font-weight: 600; letter-spacing: 0.01em; }
  .bravo-controls { font-family: "Open Sans", sans-serif; font-size: 13px; }
  .bravo-controls label { font-family: Questrial, sans-serif; font-weight: 600; font-size: 12px; color: #333; text-transform: uppercase; letter-spacing: 0.05em; }
  .bravo-controls select { font-family: "Open Sans", sans-serif; font-size: 13px; padding: 6px 9px; border: 1px solid #cfcfcf; border-radius: 4px; background: #fff; transition: border-color .15s; }
  .bravo-controls select:focus { outline: none; border-color: #c1d42f; box-shadow: 0 0 0 2px rgba(193,212,47,.35); }
  .bravo-controls .info-count { color: #666; font-size: 12px; }
  .leaflet-popup-content { font-family: "Open Sans", sans-serif; font-size: 13px; line-height: 1.45; }
  .leaflet-popup-content .venue-name { font-family: Questrial, sans-serif; font-weight: 600; font-size: 15px; color: #1f1f1f; display: block; }
  .leaflet-popup-content a { color: #5a6e0a; text-decoration: underline; }
  .leaflet-tooltip { font-family: "Open Sans", sans-serif; font-size: 12px; }
  .info.legend { font-family: "Open Sans", sans-serif; }
  .info.legend strong { font-family: Questrial, sans-serif; font-weight: 600; text-transform: uppercase; letter-spacing: 0.04em; font-size: 12px; color: #333; }
'))

js_code <- paste0('
function(el, x) {
  var map = this;
  var venues = JSON.parse(document.getElementById("bravo-venue-data").textContent);
  venues.forEach(function(v){
    if (!Array.isArray(v.cats))  v.cats  = [v.cats];
    if (!Array.isArray(v.ranks)) v.ranks = [v.ranks];
  });
  var cats   = ', cats_json,  ';
  var ICONS  = ', icons_json, ';

  var markers = L.layerGroup().addTo(map);

  // Spectral palette (used for circle markers under "All categories")
  var SPECTRAL = [
    [158,1,66], [213,62,79], [244,109,67], [253,174,97], [254,224,139],
    [255,255,191], [230,245,152], [171,221,164], [102,194,165], [50,136,189], [94,79,162]
  ];
  function lerp(a,b,t){return Math.round(a + (b-a)*t);}
  function colorForRank(rank) {
    var t = Math.max(0, Math.min(1, (rank - 1) / 19));
    var s = t * (SPECTRAL.length - 1);
    var i = Math.min(Math.floor(s), SPECTRAL.length - 2);
    var f = s - i;
    var c0 = SPECTRAL[i], c1 = SPECTRAL[i+1];
    return "rgb(" + lerp(c0[0],c1[0],f) + "," + lerp(c0[1],c1[1],f) + "," + lerp(c0[2],c1[2],f) + ")";
  }
  function radiusFor(rank) {
    return 6 + (21 - Math.min(rank, 20)) * 0.5;
  }
  function iconSizeFor(rank) {
    return Math.round(28 + (21 - Math.min(rank, 20)) * 1.6);
  }

  // Cache leaflet divIcon objects keyed by (category|size).
  // Brand-lime circular badge with the category icon on top.
  var BRAND_GREEN = "#c1d42f";
  var iconCache = {};
  function getIcon(category, rank) {
    var size = iconSizeFor(rank);
    var key  = category + "|" + size;
    if (iconCache[key]) return iconCache[key];
    var url = ICONS[category];
    if (!url) return null;
    var pad = Math.max(4, Math.round(size * 0.18));
    var inner = size - pad * 2;
    var html =
      "<div style=\\"width:" + size + "px;height:" + size + "px;border-radius:50%;" +
      "background:" + BRAND_GREEN + ";border:2px solid #fff;box-shadow:0 1px 4px rgba(0,0,0,.35);" +
      "display:flex;align-items:center;justify-content:center;\\">" +
        "<img src=\\"" + url + "\\" style=\\"width:" + inner + "px;height:" + inner + "px;\\">" +
      "</div>";
    iconCache[key] = L.divIcon({
      html: html, className: "bravo-cat-icon",
      iconSize: [size, size], iconAnchor: [size/2, size/2], popupAnchor: [0, -size/2 + 2]
    });
    return iconCache[key];
  }

  // ---- Legend ----
  var leg = L.control({position: "bottomright"});
  leg.onAdd = function() {
    var div = L.DomUtil.create("div", "info legend");
    div.style.cssText = "background:white;padding:10px 12px;border-radius:5px;box-shadow:0 1px 5px rgba(0,0,0,.25);font-size:12px;line-height:1.4;min-width:200px;";
    return div;
  };
  leg.addTo(map);

  function refreshLegend(mode, category) {
    var node = leg.getContainer();
    if (!node) return;
    if (mode === "icon" && category && ICONS[category]) {
      node.innerHTML =
        "<strong>" + category + "</strong>" +
        "<div style=\\"margin-top:8px;display:flex;align-items:center;gap:10px;\\">" +
          "<div style=\\"width:36px;height:36px;border-radius:50%;background:" + BRAND_GREEN + ";" +
            "border:2px solid #fff;box-shadow:0 1px 4px rgba(0,0,0,.35);" +
            "display:flex;align-items:center;justify-content:center;\\">" +
            "<img src=\\"" + ICONS[category] + "\\" style=\\"width:24px;height:24px;\\">" +
          "</div>" +
          "<span style=\\"font-size:11px;color:#555;\\">Badge size scales with rank</span>" +
        "</div>";
    } else {
      var stops = SPECTRAL.map(function(c, i){
        return "rgb(" + c[0] + "," + c[1] + "," + c[2] + ") " + (100 * i / (SPECTRAL.length - 1)).toFixed(1) + "%";
      }).join(", ");
      node.innerHTML =
        "<strong>Best rank in selection</strong>" +
        "<div style=\\"height:12px;border-radius:3px;margin:8px 0 4px;background:linear-gradient(to right," + stops + ");\\"></div>" +
        "<div style=\\"display:flex;justify-content:space-between;color:#555;font-size:11px;\\">" +
          "<span>1 (best)</span><span>10</span><span>20</span>" +
        "</div>" +
        "<div style=\\"margin-top:6px;color:#666;font-size:11px;\\">Circle size also scales with rank.</div>";
    }
  }

  // ---- Controls UI ----
  var venueNames = venues.map(function(v){return v.name;}).sort(function(a,b){
    return a.toLowerCase().localeCompare(b.toLowerCase());
  });

  var bar = document.createElement("div");
  bar.className = "bravo-controls";
  bar.style.cssText = "display:flex;flex-wrap:wrap;gap:14px;align-items:flex-end;margin-bottom:12px;";

  function controlBox(labelText) {
    var wrap = document.createElement("div");
    wrap.style.cssText = "display:flex;flex-direction:column;gap:4px;";
    var lbl = document.createElement("label");
    lbl.textContent = labelText;
    wrap.appendChild(lbl);
    return wrap;
  }

  var catWrap = controlBox("Category");
  var selCat = document.createElement("select");
  selCat.style.minWidth = "240px";
  cats.forEach(function(c){var o=document.createElement("option");o.value=c;o.textContent=c;selCat.appendChild(o);});
  catWrap.appendChild(selCat);
  bar.appendChild(catWrap);

  var rkWrap = controlBox("Rank range");
  var selRank = document.createElement("select");
  selRank.style.minWidth = "200px";
  [["Ignore rank (show every entry)","ignore"],
   ["Top 1 only","1"],["Top 3","3"],["Top 5","5"],["Top 10","10"],["Top 20 (all)","20"]]
    .forEach(function(r){var o=document.createElement("option");o.value=r[1];o.textContent=r[0];selRank.appendChild(o);});
  selRank.value = "ignore";
  rkWrap.appendChild(selRank);
  bar.appendChild(rkWrap);

  var vnWrap = controlBox("Zoom to venue");
  var selVenue = document.createElement("select");
  selVenue.style.minWidth = "240px";
  var oAll = document.createElement("option");
  oAll.value=""; oAll.textContent="— all visible venues —";
  selVenue.appendChild(oAll);
  venueNames.forEach(function(n){var o=document.createElement("option");o.value=n;o.textContent=n;selVenue.appendChild(o);});
  vnWrap.appendChild(selVenue);
  bar.appendChild(vnWrap);

  var info = document.createElement("div");
  info.className = "info-count";
  info.style.marginLeft = "auto";
  bar.appendChild(info);

  el.parentNode.insertBefore(bar, el);

  // ---- Drawing ----
  function popupHTML(d) {
    var rows = d.cats.map(function(c, i){
      return "<div>" + c + " <strong>#" + d.ranks[i] + "</strong></div>";
    }).join("");
    var addr = d.address || d.postcode || "";
    var link = "";
    if (d.profile_url) link = "<a href=\\"" + d.profile_url + "\\" target=\\"_blank\\">Restaurants Brighton page</a>";
    else if (d.venue_url) link = "<a href=\\"" + d.venue_url + "\\" target=\\"_blank\\">Venue website</a>";
    return "<div style=\\"min-width:240px;\\">" +
      "<span class=\\"venue-name\\">" + d.name + "</span>" +
      "<span style=\\"color:#888;font-size:12px;\\">" + addr + "</span>" +
      "<div style=\\"margin-top:6px;font-size:13px;\\">" + rows + "</div>" +
      (link ? "<div style=\\"margin-top:6px;font-size:12px;\\">" + link + "</div>" : "") +
      "</div>";
  }

  function venueMatches(d, cat, rkMode, name) {
    var bestInCat = null;
    if (cat === "All categories") {
      bestInCat = d.best_rank;
    } else {
      for (var i = 0; i < d.cats.length; i++) {
        if (d.cats[i] === cat) {
          if (bestInCat === null || d.ranks[i] < bestInCat) bestInCat = d.ranks[i];
        }
      }
      if (bestInCat === null) return null;
    }
    if (rkMode !== "ignore") {
      var maxRank = parseInt(rkMode, 10);
      if (bestInCat > maxRank) return null;
    }
    if (name && d.name !== name) return null;
    return bestInCat;
  }

  function redraw() {
    markers.clearLayers();
    var cat    = selCat.value;
    var rkMode = selRank.value;
    var name   = selVenue.value;
    var useIcon = (cat !== "All categories" && ICONS[cat]);
    var n = 0;
    var bounds = [];
    venues.forEach(function(d){
      var rank;
      try { rank = venueMatches(d, cat, rkMode, name); }
      catch(e) { return; }
      if (rank == null) return;
      try {
        var marker;
        if (useIcon) {
          marker = L.marker([d.lat, d.lon], { icon: getIcon(cat, rank) });
        } else {
          marker = L.circleMarker([d.lat, d.lon], {
            radius: radiusFor(rank),
            fillColor: colorForRank(rank),
            fillOpacity: 0.9,
            color: "#222",
            weight: 0.8
          });
        }
        marker
          .bindPopup(function(){ try { return popupHTML(d); } catch(e){ return d.name; } })
          .bindTooltip(d.name, {direction:"top"})
          .addTo(markers);
        bounds.push([d.lat, d.lon]);
        n++;
      } catch(e) {}
    });
    info.innerHTML = "<strong>" + n + "</strong> venue" + (n===1?"":"s") + " shown";
    refreshLegend(useIcon ? "icon" : "spectral", cat);

    if (name && bounds.length === 1) {
      map.flyTo(bounds[0], 16, {duration: 0.6});
    } else if (bounds.length > 1 && cat !== "All categories") {
      map.flyToBounds(bounds, {padding: [40,40], duration: 0.6, maxZoom: 14});
    }
  }

  selCat.addEventListener("change", redraw);
  selRank.addEventListener("change", redraw);
  selVenue.addEventListener("change", redraw);
  redraw();
}
')

m <- m |> onRender(js_code)

htmltools::browsable(htmltools::tagList(font_tag, style_tag, data_tag, m))
```

::: {.callout-note}
**Geocoding status.** `r sum(!is.na(venues$lat))` of `r nrow(venues)` venues plotted (post-dedupe). Missing venues are mostly delivery-only takeaways and bakeries not listed in OpenStreetMap; add postcodes manually in `bravo_2026_venues.csv` and re-run `01_geocode.R` to fill them.

Source: <https://restaurantsbrighton.co.uk/> · BRAVO 2026 awards · 71,285 votes · 18 categories.
:::
