---
title: "Brighton Restaurant Awards (BRAVO) 2026 — Interactive Map"
author: "Adam Dennett"
format:
  html:
    output-file: index.html
    page-layout: full
    toc: false
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(leaflet)
library(htmlwidgets)
library(htmltools)
library(jsonlite)

winners <- read_csv("bravo_2026_winners.csv", show_col_types = FALSE)
venues  <- read_csv("bravo_2026_venues.csv",  show_col_types = FALSE) |>
  mutate(lat = as.numeric(lat), lon = as.numeric(lon))

first_nonempty <- function(x) {
  x <- x[!is.na(x) & x != ""]
  if (length(x) == 0) "" else x[[1]]
}

venues_for_map <- winners |>
  filter(!is.na(lat), !is.na(lon)) |>
  group_by(venue_idx) |>
  summarise(
    name        = first(name),
    profile_url = first_nonempty(profile_url),
    venue_url   = first_nonempty(venue_url),
    address     = first_nonempty(address),
    postcode    = first_nonempty(postcode),
    lat         = first(lat),
    lon         = first(lon),
    rankings    = list(tibble(category = category, rank = rank)),
    best_rank   = min(rank),
    n_cats      = n(),
    .groups     = "drop"
  )

# Jitter venues sharing exact lat/lon (~5.5 m circle)
venues_for_map <- venues_for_map |>
  mutate(.coord_key = paste0(round(lat, 5), "_", round(lon, 5))) |>
  group_by(.coord_key) |>
  mutate(
    .n   = n(),
    .ix  = row_number() - 1,
    .ang = ifelse(.n > 1, 2 * pi * .ix / .n, 0),
    .r   = ifelse(.n > 1, 0.00005, 0),
    lat  = lat + .r * cos(.ang),
    lon  = lon + .r * sin(.ang) / cos(lat * pi / 180)
  ) |>
  ungroup() |>
  select(-.coord_key, -.n, -.ix, -.ang, -.r)

categories <- sort(unique(winners$category))

icon_base <- "https://img.restaurantsbrighton.co.uk"
category_icons <- c(
  "Best Brighton Restaurant"   = paste0(icon_base, "/wp-content/uploads/2019/11/best-restaurant.png"),
  "Best Sussex Restaurant"     = paste0(icon_base, "/wp-content/uploads/2016/11/best-restaurant.jpg"),
  "Best Brunch"                = paste0(icon_base, "/wp-content/uploads/2023/03/brunch-1.png"),
  "Plant Champions"            = paste0(icon_base, "/wp-content/uploads/2019/11/plant-champions.png"),
  "Best Cocktails"             = paste0(icon_base, "/wp-content/uploads/2023/03/cocktails.png"),
  "Best Brighton Pub"          = paste0(icon_base, "/wp-content/uploads/2023/03/Best-local-1.png"),
  "Family Friendly"            = paste0(icon_base, "/wp-content/uploads/2023/03/for-the-family-1.png"),
  "Best Team"                  = paste0(icon_base, "/wp-content/uploads/2023/03/best-team-1.png"),
  "Best Sussex Pub"            = paste0(icon_base, "/wp-content/uploads/2019/11/best-pub-grub.png"),
  "Best Cafe"                  = paste0(icon_base, "/wp-content/uploads/2023/03/best-cafe-1.png"),
  "Best Lunch"                 = paste0(icon_base, "/wp-content/uploads/2024/01/lunch-2.png"),
  "Best Sunday Roast"          = paste0(icon_base, "/wp-content/uploads/2023/03/sunday-roast.png"),
  "Best Wine List"             = paste0(icon_base, "/wp-content/uploads/2023/03/wine-list.png"),
  "Best International Cuisine" = paste0(icon_base, "/wp-content/uploads/2023/03/international.png"),
  "Sustainability Champions"   = paste0(icon_base, "/wp-content/uploads/2023/03/sustainable.png"),
  "Best Value"                 = paste0(icon_base, "/wp-content/uploads/2023/03/Eat-well-for-less-1.png"),
  "Best Takeaway"              = paste0(icon_base, "/wp-content/uploads/2024/01/takeaway-2.png"),
  "Sweets and Treats"          = paste0(icon_base, "/wp-content/uploads/2026/03/sweet-treat-1-4.png")
)

# Per-category badge colour. Each picks a hue that evokes the category
# (wine = burgundy, plant = green, sweets = pink, ...). Used as the
# circular badge background; the icon is rendered white on top.
category_colours <- c(
  "Best Brighton Restaurant"   = "#E63946",  # signature red
  "Best Sussex Restaurant"     = "#8E1B2C",  # deep claret
  "Best Brunch"                = "#F4A261",  # peach
  "Plant Champions"            = "#2A9D8F",  # leafy teal
  "Best Cocktails"             = "#D63384",  # cocktail pink
  "Best Brighton Pub"          = "#E1A100",  # beer amber
  "Family Friendly"            = "#4DA3FF",  # sky blue
  "Best Team"                  = "#6F42C1",  # team purple
  "Best Sussex Pub"            = "#B7791F",  # dark amber
  "Best Cafe"                  = "#8B5A2B",  # coffee brown
  "Best Lunch"                 = "#FF7043",  # warm orange
  "Best Sunday Roast"          = "#A0522D",  # roast sienna
  "Best Wine List"             = "#722F37",  # wine burgundy
  "Best International Cuisine" = "#FFB627",  # saffron
  "Sustainability Champions"   = "#588157",  # eco green
  "Best Value"                 = "#F2C200",  # gold
  "Best Takeaway"              = "#C97B3D",  # kraft brown
  "Sweets and Treats"          = "#FF8FAB"   # candy pink
)
```

Voted by 71,285 locals in March 2026. **`r nrow(venues_for_map)`** geocoded venues across **`r length(categories)`** categories.

Use the dropdowns to filter the map by category, rank range, or specific venue. Each category has its own badge colour (wine = burgundy, plant = leafy green, sweets = candy pink, and so on) — in "All categories" view, each venue takes the icon and colour of the category it ranks highest in. Badge size scales with rank.

```{r bravo-map}
venue_data <- venues_for_map |>
  rowwise() |>
  mutate(
    cats  = list(rankings$category),
    ranks = list(rankings$rank)
  ) |>
  ungroup() |>
  select(name, address, postcode, lat, lon, profile_url, venue_url,
         best_rank, n_cats, cats, ranks)

data_json    <- toJSON(venue_data, na = "null", auto_unbox = TRUE, dataframe = "rows")
cats_json    <- toJSON(c("All categories", categories), auto_unbox = TRUE)
icons_json   <- toJSON(as.list(category_icons), auto_unbox = TRUE)
colours_json <- toJSON(as.list(category_colours), auto_unbox = TRUE)

m <- leaflet(width = "100%", height = 700) |>
  addProviderTiles(providers$CartoDB.Positron) |>
  setView(lng = -0.139, lat = 50.825, zoom = 13)

data_tag <- htmltools::tags$script(
  type = "application/json",
  id   = "bravo-venue-data",
  htmltools::HTML(as.character(data_json))
)

font_tag <- htmltools::tagList(
  htmltools::tags$link(rel = "preconnect", href = "https://fonts.googleapis.com"),
  htmltools::tags$link(rel = "preconnect", href = "https://fonts.gstatic.com", crossorigin = ""),
  htmltools::tags$link(rel = "stylesheet",
    href = "https://fonts.googleapis.com/css2?family=Outfit:wght@300;400;500;600;700&family=Questrial&display=swap")
)

# Brand palette pulled from restaurantsbrighton.co.uk:
#   #4b2c4e — deep aubergine (primary brand)
#   #2e0d37 — darker plum (hover / strong text)
#   #62bed5 — accent cyan
#   #ca2bc6 — accent magenta (sparingly)
style_tag <- htmltools::tags$style(htmltools::HTML('
  body, .quarto-container, p {
    font-family: Outfit, "Helvetica Neue", Helvetica, Arial, sans-serif;
    color: #2a2a2a;
    background: #fafafa;
  }
  a { color: #4b2c4e; }
  a:hover { color: #2e0d37; }
  h1, h2, h3, h4, h5, h6, .title {
    font-family: Questrial, "Helvetica Neue", Helvetica, Arial, sans-serif;
    font-weight: 600;
    letter-spacing: 0.01em;
    color: #4b2c4e;
  }
  h1.title, .quarto-title h1 {
    font-size: 2.4rem;
    line-height: 1.15;
    border-bottom: 4px solid #4b2c4e;
    padding-bottom: 0.4rem;
    margin-bottom: 0.6rem;
  }
  .quarto-title-meta, .quarto-title-author-name { color: #4b2c4e; font-family: Questrial, sans-serif; }
  .quarto-title-meta-heading { color: #888; }
  strong { color: #2e0d37; }

  .bravo-controls {
    font-family: Outfit, sans-serif;
    font-size: 13.5px;
    background: #fff;
    border: 1px solid #ececec;
    border-radius: 8px;
    padding: 14px 16px;
    box-shadow: 0 1px 3px rgba(75,44,78,.06);
  }
  .bravo-controls label {
    font-family: Questrial, sans-serif;
    font-weight: 600;
    font-size: 11px;
    color: #4b2c4e;
    text-transform: uppercase;
    letter-spacing: 0.08em;
  }
  .bravo-controls select {
    font-family: Outfit, sans-serif;
    font-size: 13.5px;
    color: #2a2a2a;
    padding: 7px 10px;
    border: 1px solid #d8d3da;
    border-radius: 4px;
    background: #fff;
    transition: border-color .15s, box-shadow .15s;
  }
  .bravo-controls select:hover { border-color: #4b2c4e; }
  .bravo-controls select:focus {
    outline: none;
    border-color: #4b2c4e;
    box-shadow: 0 0 0 3px rgba(75,44,78,.18);
  }
  .bravo-controls .info-count { color: #4b2c4e; font-size: 13px; font-family: Questrial, sans-serif; }
  .bravo-controls .info-count strong { color: #2e0d37; font-size: 16px; }

  .leaflet-popup-content { font-family: Outfit, sans-serif; font-size: 13px; line-height: 1.45; }
  .leaflet-popup-content .venue-name {
    font-family: Questrial, sans-serif;
    font-weight: 600;
    font-size: 16px;
    color: #4b2c4e;
    display: block;
    margin-bottom: 2px;
  }
  .leaflet-popup-content a { color: #4b2c4e; text-decoration: underline; text-decoration-color: rgba(75,44,78,.4); }
  .leaflet-popup-content a:hover { color: #2e0d37; text-decoration-color: #2e0d37; }
  .leaflet-popup-content-wrapper { border-radius: 8px; box-shadow: 0 4px 16px rgba(75,44,78,.18); }
  .leaflet-popup-tip { box-shadow: none; }
  .leaflet-tooltip { font-family: Outfit, sans-serif; font-size: 12px; border-radius: 4px; }

  .info.legend {
    font-family: Outfit, sans-serif;
    border-top: 3px solid #4b2c4e;
  }
  .info.legend strong {
    font-family: Questrial, sans-serif;
    font-weight: 600;
    text-transform: uppercase;
    letter-spacing: 0.06em;
    font-size: 12px;
    color: #4b2c4e;
  }

  .callout-note {
    border-left-color: #4b2c4e !important;
    background: #fff;
  }
  .callout-note .callout-title-container { color: #4b2c4e; font-family: Questrial, sans-serif; }
'))

js_code <- paste0('
function(el, x) {
  var map = this;
  var venues = JSON.parse(document.getElementById("bravo-venue-data").textContent);
  venues.forEach(function(v){
    if (!Array.isArray(v.cats))  v.cats  = [v.cats];
    if (!Array.isArray(v.ranks)) v.ranks = [v.ranks];
  });
  var cats    = ', cats_json,    ';
  var ICONS   = ', icons_json,   ';
  var COLOURS = ', colours_json, ';

  var markers = L.layerGroup().addTo(map);

  // Spectral palette (used for circle markers under "All categories")
  var SPECTRAL = [
    [158,1,66], [213,62,79], [244,109,67], [253,174,97], [254,224,139],
    [255,255,191], [230,245,152], [171,221,164], [102,194,165], [50,136,189], [94,79,162]
  ];
  function lerp(a,b,t){return Math.round(a + (b-a)*t);}
  function colorForRank(rank) {
    var t = Math.max(0, Math.min(1, (rank - 1) / 19));
    var s = t * (SPECTRAL.length - 1);
    var i = Math.min(Math.floor(s), SPECTRAL.length - 2);
    var f = s - i;
    var c0 = SPECTRAL[i], c1 = SPECTRAL[i+1];
    return "rgb(" + lerp(c0[0],c1[0],f) + "," + lerp(c0[1],c1[1],f) + "," + lerp(c0[2],c1[2],f) + ")";
  }
  function radiusFor(rank) {
    return 6 + (21 - Math.min(rank, 20)) * 0.5;
  }
  function iconSizeFor(rank) {
    return Math.round(28 + (21 - Math.min(rank, 20)) * 1.6);
  }

  // Cache leaflet divIcon objects keyed by (category|size).
  // Per-category coloured circular badge with the icon rendered white on top.
  var BRAND_AUBERGINE = "#4b2c4e";
  function colourFor(category) {
    return COLOURS[category] || BRAND_AUBERGINE;
  }
  var iconCache = {};
  function getIcon(category, rank) {
    var size = iconSizeFor(rank);
    var key  = category + "|" + size;
    if (iconCache[key]) return iconCache[key];
    var url = ICONS[category];
    if (!url) return null;
    var bg = colourFor(category);
    // Solid category-colour disc with the icon on top. The icon PNGs have
    // transparent backgrounds, so the colour shows through around the
    // grey + lime line-art and the badge looks like a single tinted disc.
    var pad = Math.max(3, Math.round(size * 0.12));
    var inner = size - pad * 2;
    var html =
      "<div style=\\"width:" + size + "px;height:" + size + "px;border-radius:50%;" +
      "background:" + bg + ";border:2px solid #fff;box-shadow:0 1px 4px rgba(0,0,0,.35);" +
      "display:flex;align-items:center;justify-content:center;\\">" +
        "<img src=\\"" + url + "\\" style=\\"width:" + inner + "px;height:" + inner + "px;\\">" +
      "</div>";
    iconCache[key] = L.divIcon({
      html: html, className: "bravo-cat-icon",
      iconSize: [size, size], iconAnchor: [size/2, size/2], popupAnchor: [0, -size/2 + 2]
    });
    return iconCache[key];
  }

  // ---- Legend ----
  var leg = L.control({position: "bottomright"});
  leg.onAdd = function() {
    var div = L.DomUtil.create("div", "info legend");
    div.style.cssText = "background:white;padding:10px 12px;border-radius:5px;box-shadow:0 1px 5px rgba(0,0,0,.25);font-size:12px;line-height:1.4;min-width:200px;";
    return div;
  };
  leg.addTo(map);

  function badgeHTML(category, px) {
    var inner = Math.round(px * 0.78);
    return "<div style=\\"width:" + px + "px;height:" + px + "px;border-radius:50%;" +
      "background:" + colourFor(category) + ";border:1.5px solid #fff;" +
      "box-shadow:0 1px 3px rgba(0,0,0,.25);display:flex;align-items:center;" +
      "justify-content:center;flex:0 0 auto;\\">" +
        "<img src=\\"" + ICONS[category] + "\\" style=\\"width:" + inner + "px;height:" + inner + "px;\\">" +
      "</div>";
  }

  function refreshLegend(mode, category) {
    var node = leg.getContainer();
    if (!node) return;
    if (mode === "icon" && category && ICONS[category]) {
      node.innerHTML =
        "<strong>" + category + "</strong>" +
        "<div style=\\"margin-top:8px;display:flex;align-items:center;gap:10px;\\">" +
          badgeHTML(category, 36) +
          "<span style=\\"font-size:11px;color:#555;\\">Badge size scales with rank</span>" +
        "</div>";
    } else {
      // "All categories" mode — colour swatch grid keying each badge colour
      // to its category, since each venue is drawn with the icon/colour of
      // the category it ranks highest in.
      var rows = "";
      for (var i = 1; i < cats.length; i++) {
        var c = cats[i];
        rows +=
          "<div style=\\"display:flex;align-items:center;gap:6px;font-size:11px;color:#333;\\">" +
            badgeHTML(c, 18) +
            "<span>" + c + "</span>" +
          "</div>";
      }
      node.innerHTML =
        "<strong>All categories</strong>" +
        "<div style=\\"margin-top:6px;font-size:11px;color:#666;line-height:1.35;\\">" +
          "Each venue uses the icon &amp; colour of the category it ranks <em>highest</em> in." +
        "</div>" +
        "<div style=\\"margin-top:8px;display:grid;grid-template-columns:1fr 1fr;" +
        "gap:5px 12px;max-width:360px;\\">" + rows + "</div>";
    }
  }

  // ---- Controls UI ----
  var venueNames = venues.map(function(v){return v.name;}).sort(function(a,b){
    return a.toLowerCase().localeCompare(b.toLowerCase());
  });

  var bar = document.createElement("div");
  bar.className = "bravo-controls";
  bar.style.cssText = "display:flex;flex-wrap:wrap;gap:14px;align-items:flex-end;margin-bottom:12px;";

  function controlBox(labelText) {
    var wrap = document.createElement("div");
    wrap.style.cssText = "display:flex;flex-direction:column;gap:4px;";
    var lbl = document.createElement("label");
    lbl.textContent = labelText;
    wrap.appendChild(lbl);
    return wrap;
  }

  var catWrap = controlBox("Category");
  var selCat = document.createElement("select");
  selCat.style.minWidth = "240px";
  cats.forEach(function(c){var o=document.createElement("option");o.value=c;o.textContent=c;selCat.appendChild(o);});
  catWrap.appendChild(selCat);
  bar.appendChild(catWrap);

  var rkWrap = controlBox("Rank range");
  var selRank = document.createElement("select");
  selRank.style.minWidth = "200px";
  [["Ignore rank (show every entry)","ignore"],
   ["Top 1 only","1"],["Top 3","3"],["Top 5","5"],["Top 10","10"],["Top 20 (all)","20"]]
    .forEach(function(r){var o=document.createElement("option");o.value=r[1];o.textContent=r[0];selRank.appendChild(o);});
  selRank.value = "ignore";
  rkWrap.appendChild(selRank);
  bar.appendChild(rkWrap);

  var vnWrap = controlBox("Zoom to venue");
  var selVenue = document.createElement("select");
  selVenue.style.minWidth = "240px";
  var oAll = document.createElement("option");
  oAll.value=""; oAll.textContent="— all visible venues —";
  selVenue.appendChild(oAll);
  venueNames.forEach(function(n){var o=document.createElement("option");o.value=n;o.textContent=n;selVenue.appendChild(o);});
  vnWrap.appendChild(selVenue);
  bar.appendChild(vnWrap);

  var info = document.createElement("div");
  info.className = "info-count";
  info.style.marginLeft = "auto";
  bar.appendChild(info);

  el.parentNode.insertBefore(bar, el);

  // ---- Drawing ----
  function popupHTML(d) {
    var rows = d.cats.map(function(c, i){
      return "<div>" + c + " <strong>#" + d.ranks[i] + "</strong></div>";
    }).join("");
    var addr = d.address || d.postcode || "";
    var link = "";
    if (d.profile_url) link = "<a href=\\"" + d.profile_url + "\\" target=\\"_blank\\">Restaurants Brighton page</a>";
    else if (d.venue_url) link = "<a href=\\"" + d.venue_url + "\\" target=\\"_blank\\">Venue website</a>";
    return "<div style=\\"min-width:240px;\\">" +
      "<span class=\\"venue-name\\">" + d.name + "</span>" +
      "<span style=\\"color:#888;font-size:12px;\\">" + addr + "</span>" +
      "<div style=\\"margin-top:6px;font-size:13px;\\">" + rows + "</div>" +
      (link ? "<div style=\\"margin-top:6px;font-size:12px;\\">" + link + "</div>" : "") +
      "</div>";
  }

  function venueMatches(d, cat, rkMode, name) {
    var bestInCat = null;
    if (cat === "All categories") {
      bestInCat = d.best_rank;
    } else {
      for (var i = 0; i < d.cats.length; i++) {
        if (d.cats[i] === cat) {
          if (bestInCat === null || d.ranks[i] < bestInCat) bestInCat = d.ranks[i];
        }
      }
      if (bestInCat === null) return null;
    }
    if (rkMode !== "ignore") {
      var maxRank = parseInt(rkMode, 10);
      if (bestInCat > maxRank) return null;
    }
    if (name && d.name !== name) return null;
    return bestInCat;
  }

  // For "All categories" view, pick the category where this venue ranks
  // highest (lowest rank number). Tie-break is the order categories appear.
  function topCategoryFor(d) {
    var bestI = 0;
    for (var i = 1; i < d.ranks.length; i++) {
      if (d.ranks[i] < d.ranks[bestI]) bestI = i;
    }
    return d.cats[bestI];
  }

  function redraw() {
    markers.clearLayers();
    var cat    = selCat.value;
    var rkMode = selRank.value;
    var name   = selVenue.value;
    var n = 0;
    var bounds = [];
    venues.forEach(function(d){
      var rank;
      try { rank = venueMatches(d, cat, rkMode, name); }
      catch(e) { return; }
      if (rank == null) return;
      // Choose which icon to render: if the user has picked a specific
      // category, use that one; otherwise use the top-ranked category for this venue.
      var iconCat = (cat === "All categories") ? topCategoryFor(d) : cat;
      try {
        var marker;
        if (ICONS[iconCat]) {
          marker = L.marker([d.lat, d.lon], { icon: getIcon(iconCat, rank) });
        } else {
          // Fallback path — every category has an icon, so this is rarely hit.
          marker = L.circleMarker([d.lat, d.lon], {
            radius: radiusFor(rank),
            fillColor: colorForRank(rank),
            fillOpacity: 0.9,
            color: "#222",
            weight: 0.8
          });
        }
        marker
          .bindPopup(function(){ try { return popupHTML(d); } catch(e){ return d.name; } })
          .bindTooltip(d.name, {direction:"top"})
          .addTo(markers);
        bounds.push([d.lat, d.lon]);
        n++;
      } catch(e) {}
    });
    info.innerHTML = "<strong>" + n + "</strong> venue" + (n===1?"":"s") + " shown";
    refreshLegend(cat === "All categories" ? "all" : "icon", cat);

    if (name && bounds.length === 1) {
      map.flyTo(bounds[0], 16, {duration: 0.6});
    } else if (bounds.length > 1 && cat !== "All categories") {
      map.flyToBounds(bounds, {padding: [40,40], duration: 0.6, maxZoom: 14});
    }
  }

  selCat.addEventListener("change", redraw);
  selRank.addEventListener("change", redraw);
  selVenue.addEventListener("change", redraw);
  redraw();
}
')

m <- m |> onRender(js_code)

htmltools::browsable(htmltools::tagList(font_tag, style_tag, data_tag, m))
```

::: {.callout-note}
**Geocoding status.** `r sum(!is.na(venues$lat))` of `r nrow(venues)` venues plotted (post-dedupe). Missing venues are mostly delivery-only takeaways and bakeries not listed in OpenStreetMap; add postcodes manually in `bravo_2026_venues.csv` and re-run `01_geocode.R` to fill them.

Source: <https://restaurantsbrighton.co.uk/> · BRAVO 2026 awards · 71,285 votes · 18 categories.
:::
